---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {forager}

> ***Forager** (noun)*
>
> *A person that goes from place to place searching for things that they
> can eat or use.*[^1]

> ***Ager** (noun)*
>
> *A person that calls from place to place searching for payment before
> insurance can refuse.*[^2]

<br><br>

<!-- badges: start -->

[![R-CMD-check](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml)
[![repo status:
WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

<!-- badges: end -->

The goal of {forager} is to provide tools for common healthcare revenue
cycle management processes and analyses.

## Installation

You can install the development version of forager from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/forager")
```

## Calculating Days in AR

This is a basic example of a monthly Days in Accounts Receivables
calculation:

```{r example}
library(forager)

# Example data frame
dar_mon_ex
```

```{r}
dar_month(dar_mon_ex, date, gct, earb, dart = 39.445) |> 
  dplyr::select(!c(date, nmon, ndip, actual:radiff))
```

## Code of Conduct

Please note that the forager project is released with a [Contributor
Code of
Conduct](https://andrewallenbruce.github.io/forager/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

[^1]: <https://dictionary.cambridge.org/dictionary/english/forager>

[^2]: Bruce, A.A.
