---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 150, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# forager <a href="https://andrewallenbruce.github.io/forager/"><img src="man/figures/logo.svg" align="right" height="200"/></a>

> ***Forager** (noun)*
>
> *A person that goes from place to place searching for things that they
> can eat or use.*[^1]

> ***Ager** (noun)*
>
> *A person that calls from place to place searching for payment before
> insurance can refuse.*[^2]

<br>

<!-- badges: start -->

[![R-CMD-check](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml)
[![License:
MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code
size](https://img.shields.io/github/languages/code-size/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager)
[![last
commit](https://img.shields.io/github/last-commit/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager/commits/master)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/forager/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/forager?branch=master)
<!-- badges: end -->

## Installation

You can install the development version of `forager` from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/forager")
```

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(clock)
library(forager)
library(fuimus)
```

## Foundation: Time Measurement

Everything in a Healthcare RCM workflow is built upon the bedrock of time measurement. 

   *  Task $a$ is created at time $t$.
   *  Subtask $a_1$ is assigned at time $t_1$ to responsible party $x_1$.
   *  Subtask $a_2$ is assigned at time $t_2$ to responsible party $x_2$.
   *  So on, and so forth until...
   *  Task $a_i$ is completed at time $t_i$.
   
Measuring the amount of time between each step becomes crucial in identifying workflow issues.

### Example: The Lifecycle of a Claim 

   * **Provider Lag**: Days between *Date of Service* and *Date of Release*
   * **Billing Lag**:  Days between *Date of Release* and *Date of Submission*
   * **Acceptance Lag**:  Days between *Date of Submission* and *Date of Acceptance*
   * **Payment Lag**: Days between *Date of Acceptance* and *Date of Adjudication*
   * **Days in AR**: Days between *Date of Release* and *Date of Adjudication*

<br>

```{r, echo=TRUE, warning=FALSE}
x <- forager::generate_data(1500)

mean(x$days_in_ar, na.rm = TRUE)
```
<br>

```{r echo=TRUE}
x_pvt <- x |> 
  select(clm_id:date_recon) |> 
  pivot_longer(
    cols      = starts_with("date"), 
    names_to  = "date_type", 
    values_to = "date") |> 
  mutate(date_lag = lead(date) - date,
         date_lag = lag(date_lag, order_by = date),
         date_type = str_remove_all(date_type, "date_"),
         date_type = case_match(
           date_type,
           "srvc" ~ "Service",
           "rlse" ~ "Release",
           "submit" ~ "Submission",
           "accept" ~ "Acceptance",
           "adjud" ~ "Adjudication",
           "recon" ~ "Reconciliation"),
         date_type = fct_relevel(
           date_type, 
           "Service", 
           "Release", 
           "Submission", 
           "Acceptance", 
           "Adjudication", 
           "Reconciliation"), 
         .by = clm_id)

x_pvt
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year  = get_year(date_srvc),
    month = date_month_factor(date_srvc)) |> 
  summarise(
    n_claims    = n(), 
    balance     = sum(balance, na.rm = TRUE),
    days_rlse   = mean(days_rlse, na.rm = TRUE), 
    days_submit = mean(days_submit, na.rm = TRUE),
    days_accept = mean(days_accept, na.rm = TRUE),
    days_adjud  = mean(days_adjud, na.rm = TRUE),
    days_recon  = mean(days_recon, na.rm = TRUE),
    days_in_ar  = mean(days_in_ar, na.rm = TRUE), 
    .groups = "drop")
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year  = get_year(date_srvc),
    nqtr = quarter(date_srvc)) |> 
  summarise(
    n_claims    = n(), 
    balance     = sum(balance, na.rm = TRUE),
    days_rlse   = mean(days_rlse, na.rm = TRUE), 
    days_submit = mean(days_submit, na.rm = TRUE),
    days_accept = mean(days_accept, na.rm = TRUE),
    days_adjud  = mean(days_adjud, na.rm = TRUE),
    days_recon  = mean(days_recon, na.rm = TRUE),
    days_in_ar  = mean(days_in_ar, na.rm = TRUE), 
    .groups = "drop")
```


## Aging Calculation

```{r echo=TRUE}
x |> 
  bin_aging(days_in_ar, bin_type = "chop") |> 
  group_by(aging_bin) |> 
  summarise(
    n_claims = n(),
    balance = roundup(sum(balance, na.rm = TRUE)), 
    .groups = "drop")

x |> 
  bin_aging(days_in_ar, bin_type = "case") |> 
  group_by(aging_bin) |> 
  summarise(
    n_claims = n(),
    balance = roundup(sum(balance, na.rm = TRUE)), 
    .groups = "drop")
```

## Days in AR Monthly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 290000:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "month")
```

<br>

## Days in AR Quarterly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 285500:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "quarter")
```


## Code of Conduct

Please note that the `forager` project is released with a [Contributor
Code of
Conduct](https://andrewallenbruce.github.io/forager/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

[^1]: <https://dictionary.cambridge.org/dictionary/english/forager>

[^2]: Me.

