---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 150, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# forager <a href="https://andrewallenbruce.github.io/forager/"><img src="man/figures/logo.svg" align="right" height="200"/></a>

> ***Forager** (noun)*
>
> *A person that goes from place to place searching for things that they
> can eat or use.*[^1]

> ***Ager** (noun)*
>
> *A person that calls from place to place searching for payment before
> insurance can refuse.*[^2]

<br>

<!-- badges: start -->

[![R-CMD-check](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml)
[![License:
MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code
size](https://img.shields.io/github/languages/code-size/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager)
[![last
commit](https://img.shields.io/github/last-commit/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager/commits/master)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/forager/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/forager?branch=master)
<!-- badges: end -->

## Installation

You can install the development version of `forager` from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/forager")
```

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(clock)
library(forager)
library(fuimus)
```

## The Lifecycle of a Claim 

    * <b>Provider Lag</b>:    Date of Service - Date of Release
    * <b>Billing Lag</b>:     Date of Release - Date of Submission
    * <b>Acceptance Lag</b>:  Date of Submission - Date of Acceptance
    * <b>Payment Lag</b>:     Date of Acceptance - Date of Adjudication
    * <b>Days in AR</b>:      Date of Release - Date of Adjudication*


<br>

```{r, echo=TRUE, warning=FALSE}
x <- forager::generate_data(1500)
x
```
<br>

```{r echo=TRUE}
x_pvt <- x |> 
  select(claimid:date_reconciliation) |> 
  pivot_longer(
    cols      = starts_with("date"), 
    names_to  = "date_type", 
    values_to = "date") |> 
  mutate(
    date_lag = lead(date) - date,
    date_lag = lag(date_lag, order_by = date),
    date_type = stringr::str_to_sentence(
      str_remove_all(date_type, "date_")),
    date_type = fct_relevel(
      date_type, 
      "Service", 
      "Release",
      "Submission", 
      "Acceptance", 
      "Adjudication", 
      "Reconciliation"), 
    .by = claimid)

x_pvt
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = get_year(date_service),
    month = date_month_factor(date_service)) |> 
  summarise(
    Claims = n(), 
    Balance = sum(balance, na.rm = TRUE),
    Release = as.numeric(mean((date_release - date_service), na.rm = TRUE)), 
    Submission = as.numeric(mean((date_submission - date_release), na.rm = TRUE)),
    Acceptance = as.numeric(mean((date_acceptance - date_submission), na.rm = TRUE)),
    Adjudication  = as.numeric(mean((date_adjudication - date_acceptance), na.rm = TRUE)),
    Reconciliation = as.numeric(mean((date_reconciliation - date_adjudication), na.rm = TRUE)),
    Average_DAR = as.numeric(mean((date_reconciliation - date_service), na.rm = TRUE)), 
    .groups = "drop")
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year  = get_year(date_service),
    nqtr = quarter(date_service)) |> 
  summarise(
    Claims = n(), 
    Balance = sum(balance, na.rm = TRUE),
    Release = as.numeric(mean((date_release - date_service), na.rm = TRUE)), 
    Submission = as.numeric(mean((date_submission - date_release), na.rm = TRUE)),
    Acceptance = as.numeric(mean((date_acceptance - date_submission), na.rm = TRUE)),
    Adjudication  = as.numeric(mean((date_adjudication - date_acceptance), na.rm = TRUE)),
    Reconciliation = as.numeric(mean((date_reconciliation - date_adjudication), na.rm = TRUE)),
    Average_DAR = as.numeric(mean((date_reconciliation - date_service), na.rm = TRUE)), 
    .groups = "drop")
```


## Aging Calculation

```{r echo=TRUE}
x |> 
  mutate(days_in_ar = as.numeric((date_reconciliation - date_service))) |> 
  bin_aging(days_in_ar, bin_type = "chop") |> 
  group_by(aging_bin) |> 
  summarise(
    n_claims = n(),
    balance = roundup(sum(balance, na.rm = TRUE)), 
    .groups = "drop")

x |> 
  mutate(days_in_ar = as.numeric((date_reconciliation - date_service))) |> 
  bin_aging(days_in_ar, bin_type = "case") |> 
  group_by(aging_bin) |> 
  summarise(
    n_claims = n(),
    balance = roundup(sum(balance, na.rm = TRUE)), 
    .groups = "drop")
```

## Days in AR Monthly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 290000:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "month")
```

<br>

## Days in AR Quarterly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 285500:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "quarter")
```


## Code of Conduct

Please note that the `forager` project is released with a [Contributor
Code of
Conduct](https://andrewallenbruce.github.io/forager/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

[^1]: <https://dictionary.cambridge.org/dictionary/english/forager>

[^2]: Me.

