---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# forager <a href="#"><img src="man/figures/logo.svg" align="right" width="25%" min-width="120px"/></a>

> ***Forager** (noun)*
>
> *A person that goes from place to place searching for things that they
> can eat or use.*[^1]

> ***Ager** (noun)*
>
> *A person that calls from place to place searching for payment before
> insurance can refuse.*[^2]

<br>

<!-- badges: start -->

![GitHub R package version](https://img.shields.io/github/r-package/v/andrewallenbruce/forager?style=flat-square&logo=R&label=Package&color=%23192a38)
[![R-CMD-check](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager/commits/master)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/forager/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/forager?branch=master)

<!-- badges: end -->

## Installation

You can install the development version of `forager` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/forager")
```

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ymd)
library(forager)
library(fuimus)
```

## The Lifecycle of a Claim 

```{r, echo=TRUE, warning=FALSE}
(x <- mock_claims(15000))
```

<br>

```{r echo=TRUE}
(x <- prep_claims(x))
```

<br>

```{r}
summarise_claims(x) |> 
  glimpse()
```



```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    month = month(date_service),
    payer
  ) |>
  summarise_claims() |> 
  arrange(payer) |>
  select(year, month, payer, n_claims, ending_ar, mean_dar)
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = get_year(date_service),
    qtr = quarter(date_service),
    payer
    ) |>
  summarise_claims() |> 
  arrange(payer) |>
  select(year, qtr, payer, n_claims, ending_ar, mean_dar)
```

## Days in AR Calculation

> Monthly

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 290000:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "month")
```

<br>

> Quarterly

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 285500:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "quarter")
```


## Code of Conduct

Please note that the `forager` project is released with a [Contributor
Code of
Conduct](https://andrewallenbruce.github.io/forager/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

[^1]: <https://dictionary.cambridge.org/dictionary/english/forager>

[^2]: Me.

