---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `forager` <a href="https://andrewallenbruce.github.io/forager/"><img src="man/figures/logo.svg" align="right" height="500" /></a>

> ***Forager** (noun)*
>
> *A person that goes from place to place searching for things that they
> can eat or use.*[^1]

> ***Ager** (noun)*
>
> *A person that calls from place to place searching for payment before
> insurance can refuse.*[^2]

<br>

<!-- badges: start -->

[![R-CMD-check](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/forager/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![repo status: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/forager.svg)](https://github.com/andrewallenbruce/forager/commits/master)

<!-- badges: end -->

The goal of {forager} is to provide a suite of tools for the analysis of common healthcare revenue
cycle management Key Performance Indicators (KPIs).

## Installation

You can install the development version of forager from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/forager")
```

## Days in AR Calculation

This is a basic example of a monthly Days in AR calculation:

```{r example}
library(forager)

# Example data frame
dar_mon_ex |> 
  knitr::kable(
    digits = 2, 
    col.names = c(
      "Month", 
      "Gross Charges", 
      "Ending AR Balance"))
```


```{r}
dar_month_2022 <- dar_month(dar_mon_ex, date, gct, earb, dart = 35)

dar_month_2022
```

```{r eval=FALSE, include=FALSE}
# Create df for gt_plt_bar_stack
dar_month_2022_pct <- dar_month_2022 |>
  dplyr::mutate(gct_pct = (gct / (gct + earb) * 100),
         earb_pct = (earb / (gct + earb) * 100)) |>
  dplyr::select(month, gct_pct, earb_pct) |>
  tidyr::pivot_longer(-month, names_to = "measure", values_to = "percentage") |>
  dplyr::group_by(month) |>
  dplyr::summarize(list_data = list(percentage))

# Right join the two data frames
dar_month_2022_join <- dplyr::right_join(dar_month_2022, 
                                         dar_month_2022_pct, 
                                         by = "month")

# Create new copy cols for gt_plt_bullet
dar_month_2022_gt <- dar_month_2022_join |> 
  dplyr::select(month, 
                gct, 
                earb, 
                earb_trg, 
                dar, 
                pass,
                list_data) |>
  dplyr::mutate(target_col = earb, 
                plot_col = earb_trg)

# Create gt table
dar_month_2022_gt |> 
  gt::gt(rowname_col = "month") |>
  gt::cols_label(gct = "Gross Charges",
                 earb = "Ending AR",
                 earb_trg = "Optimal AR",
                 dar = "Days in AR",
                 pass = "Pass",
                 plot_col = "Optimal AR Threshold") |>
  gt::fmt_number(columns = dar) |>
  gt::fmt_currency(columns = c(gct, earb, earb_trg)) |>
  gtExtras::gt_plt_bullet(column = plot_col, target = target_col, palette = c("#8ca0aa", "black"), width = 65) |>
  gtExtras::gt_plt_bar_stack(list_data, width = 50, labels = c("Charges (%) ", " AR (%)"), palette = c("#2c3e50", "#8ca0aa")) |>
  gtExtras::gt_badge(pass, palette = c("FALSE" = "red")) |> 
  gt::tab_style(style = gt::cell_text(color = "red", weight = "bold"), locations = gt::cells_body(columns = pass, rows = pass == "FALSE")) |>
  gtExtras::gt_theme_538()
```


## Code of Conduct

Please note that the forager project is released with a [Contributor
Code of
Conduct](https://andrewallenbruce.github.io/forager/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

[^1]: <https://dictionary.cambridge.org/dictionary/english/forager>

[^2]: Me.
