---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
)
options(scipen = 999)

# Personal libraries
library(forager)
library(fuimus)

# Data wrangling
library(clock)
library(dplyr)
library(tidyr)
library(forcats)
library(ymd)

# Data visualization
library(gt)
library(gtExtras)
library(ggplot2)
library(ggrepel)
library(scales)
```

## Introduction

Date of Service (DOS) to Date of Reconciliation is a critical metric for Revenue Cycle Management. The time it takes to process a claim can have a significant impact on cash flow. This vignette demonstrates how to calculate the average days in accounts receivable (AR) for a medical practice.

## Definitions

Date of Service: The date a patient receives medical services.

Date of Release: The date a claim is released for billing.

Date of Submission: The date a claim is submitted to the payer.

Date of Acceptance: The date a claim is accepted by the payer.

Date of Adjudication: The date a claim is adjudicated by the payer.

Date of Reconciliation: The date a claim is reconciled by the medical practice.

## The Lifecycle of a Claim 

  * <b>Provider Lag</b>:    Date of Service - Date of Release
  * <b>Billing Lag</b>:     Date of Release - Date of Submission
  * <b>Acceptance Lag</b>:  Date of Submission - Date of Acceptance
  * <b>Payment Lag</b>:     Date of Acceptance - Date of Adjudication
  * <b>Days in AR</b>:      Date of Release - Date of Adjudication
  

<br>

```{r, echo=TRUE, warning=FALSE}
# Balances, when zero, add net payment and adjustments
# Payment and adjustments should be a percentage of the balance, equal to one
(x <- mock_claims(15000))
```

<br>

```{r echo=TRUE}
(x <- prep_claims(x))
```

<br>

```{r}
summarise_claims(x) |> 
  glimpse()
```



```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    month = month(date_service)
    ) |>
  summarise_claims()
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    quarter = quarter(date_service)
    ) |>
  summarise_claims()
```


```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    month = month(date_service),
    aging_bin
    ) |>
  summarise_claims()
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    quarter = quarter(date_service),
    payer
    ) |>
  summarise_claims()
```






# Average Days in AR

## Monthly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 290000:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "month")
```

<br>

## Quarterly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 285500:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "quarter")
```

<br>
