---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
)
options(scipen = 999)

# Personal libraries
library(forager)
library(fuimus)

# Data wrangling
library(clock)
library(dplyr)
library(tidyr)
library(forcats)
library(ymd)

# Data visualization
library(gt)
library(gtExtras)
library(ggplot2)
library(ggrepel)
library(scales)
```

## Introduction

Date of Service (DOS) to Date of Reconciliation is a critical metric for Revenue Cycle Management. The time it takes to process a claim can have a significant impact on cash flow. This vignette demonstrates how to calculate the average days in accounts receivable (AR) for a medical practice.

## Definitions

Date of Service: The date a patient receives medical services.

Date of Release: The date a claim is released for billing.

Date of Submission: The date a claim is submitted to the payer.

Date of Acceptance: The date a claim is accepted by the payer.

Date of Adjudication: The date a claim is adjudicated by the payer.

Date of Reconciliation: The date a claim is reconciled by the medical practice.

## The Lifecycle of a Claim 

  * <b>Provider Lag</b>:    Date of Service - Date of Release
  * <b>Billing Lag</b>:     Date of Release - Date of Submission
  * <b>Acceptance Lag</b>:  Date of Submission - Date of Acceptance
  * <b>Payment Lag</b>:     Date of Acceptance - Date of Adjudication
  * <b>Days in AR</b>:      Date of Release - Date of Adjudication
  

<br>

```{r, echo=TRUE, warning=FALSE}
# Balances, when zero, add net payment and adjustments
# Payment and adjustments should be a percentage of the balance, equal to one
(x <- mock_claims(15000))
```

<br>

```{r echo=TRUE}
long <- x |> 
  pivot_longer(
    cols      = starts_with("date"), 
    names_to  = "date_type", 
    names_prefix = "date_",
    values_to = "date") |> 
  mutate(
    date_type = fct_relevel(
      date_type, 
      "service", 
      "release",
      "submission", 
      "acceptance", 
      "adjudication", 
      "reconciliation"), 
    days = as.numeric(lead(date) - date),
    days = lag(days, order_by = date),
    .by = claimid) |> 
  arrange(claimid, date_type)

long
```

<br>

```{r}
x <- long |> 
  pivot_wider(
    names_from = date_type,
    names_glue = "{.value}_{date_type}",
    values_from = c(date, days)
  ) |> 
  remove_quiet() |> 
  rowwise() |> 
  mutate(days_in_ar = if_else(
      !is.na(date_reconciliation), 
      as.numeric((date_reconciliation - date_service)),
      as.numeric((date_adjudication - date_service))
  )) |> 
  ungroup() |> 
  nest(dates = c(date_release, date_submission, date_acceptance, date_adjudication, date_reconciliation)) |>
  bin_aging(days_in_ar)
x
```


```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    month = month(date_service)
    ) |>
  summarise(
    claims             = n(), 
    balance            = sum_na(balance),
    avg_release        = mean_na(days_release), 
    avg_submission     = mean_na(days_submission),
    avg_acceptance     = mean_na(days_acceptance),
    avg_adjudication   = mean_na(days_adjudication),
    avg_reconciliation = mean_na(days_reconciliation),
    avg_days_in_ar     = mean_na(days_in_ar),
    .groups = "drop")
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    quarter = quarter(date_service)
    ) |>
  summarise(
    claims             = n(), 
    balance            = sum_na(balance),
    avg_release        = mean_na(days_release), 
    avg_submission     = mean_na(days_submission),
    avg_acceptance     = mean_na(days_acceptance),
    avg_adjudication   = mean_na(days_adjudication),
    avg_reconciliation = mean_na(days_reconciliation),
    avg_days_in_ar     = mean_na(days_in_ar),
    .groups = "drop")
```


```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    month = month(date_service),
    payer,
    aging_bin
    ) |>
  summarise(
    claims             = n(), 
    balance            = sum_na(balance),
    avg_release        = mean_na(days_release), 
    avg_submission     = mean_na(days_submission),
    avg_acceptance     = mean_na(days_acceptance),
    avg_adjudication   = mean_na(days_adjudication),
    avg_reconciliation = mean_na(days_reconciliation),
    avg_days_in_ar     = mean_na(days_in_ar),
    .groups = "drop")
```

<br>

```{r echo=TRUE}
x |> 
  group_by(
    year = year(date_service),
    quarter = quarter(date_service),
    payer,
    aging_bin
    ) |>
  summarise(
    claims             = n(), 
    balance            = sum_na(balance),
    avg_release        = mean_na(days_release), 
    avg_submission     = mean_na(days_submission),
    avg_acceptance     = mean_na(days_acceptance),
    avg_adjudication   = mean_na(days_adjudication),
    avg_reconciliation = mean_na(days_reconciliation),
    avg_days_in_ar     = mean_na(days_in_ar),
    .groups = "drop")
```






# Average Days in AR

## Monthly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 290000:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "month")
```

<br>

## Quarterly Calculation

```{r echo=TRUE}
tibble(
  date = date_build(2024, 1:12),
  gct  = rpois(12, 250000:400000),
  earb = rpois(12, 285500:400000)
  ) |> 
  avg_dar(
    date, 
    gct, 
    earb, 
    dart = 35,
    by = "quarter")
```

<br>
