---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )

library(forager)
library(dplyr)
library(tidyr)
library(gt)
```

## Introduction

The `forager` package is a collection of functions that are useful for healthcare revenue cycle analysis. 

## DAR

Days in Accounts Receivable (also known as Days in AR or simply DAR) is a common financial metric belonging to a group of ratios called **efficiency ratios**. The calculation measures the average amount of time it takes for a business to collect money owed from the responsible party for services rendered and billed.

As its name implies, the unit of measurement employed by this particular metric is days, or rather the average number of days from the moment a physician provides a service until the patient or guarantor pays for that service. This number can tell you much about the financial health of the business.

The formula for calculating DAR is: 

```{r}
dar_ex()
```



```{r}
avg_dar(
  df     = dar_ex(),
  date   = date,
  gct    = gross_charges,
  earb   = ending_ar,
  dart   = 35,
  period = "month"
) |> 
  gt()
```

```{r}
avg_dar(
  df     = dar_ex(),
  date   = date,
  gct    = gross_charges,
  earb   = ending_ar,
  dart   = 39,
  period = "quarter"
) |> 
  gt()
```

## Aging Bins

```{r}
binned <- bin_aging(
  df = load_ex("aging_ex"),
  date = dos
  ) |>
  dplyr::select(
    dos:ins_class,
    dar:aging_bin
    )

binned
```

```{r}
binned |>
   dplyr::arrange(aging_bin) |>
   dplyr::summarise(n_claims = dplyr::n(),
                    balance = sum(charges),
                    .by = aging_bin) |>
   dplyr::mutate(
     pct_claims = n_claims / sum(n_claims),
     pct_balance = balance / sum(balance)) |> 
  gt() |> 
  fmt_percent(columns = pct_claims:pct_balance)
```


```{r}
binned |>
  dplyr::arrange(aging_bin, ins_name) |>
  dplyr::summarise(
    n_claims = dplyr::n(),
    balance = sum(charges),
    .by = c(aging_bin, ins_name)
  ) |>
  dplyr::mutate(pct_claims = n_claims / sum(n_claims),
                pct_balance = balance / sum(balance)) |>
  gt() |>
  fmt_percent(columns = pct_claims:pct_balance)
```


```{r}
binned |>
  dplyr::arrange(ins_name, aging_bin) |>
  dplyr::summarise(
    n_claims = dplyr::n(),
    balance = sum(charges),
    .by = c(aging_bin, ins_name)
  ) |>
  dplyr::mutate(pct_claims = n_claims / sum(n_claims),
                pct_balance = balance / sum(balance),
                .by = ins_name) |>
  gt() |>
  fmt_percent(columns = pct_claims:pct_balance)
```
