---
title: "DAR Formulas"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )

library(forager)
library(dplyr)
library(tidyr)
library(gt)
```

## Days in Accounts Receivable

Days in Accounts Receivable is a mathematical formula that calculates the average number of days it takes a business to collect money that it is owed. The DAR number should be low. A high DAR number tells you that there is a problem in your revenue cycle.

Days in Accounts Receivable (also known as Days in AR or simply DAR) is a common financial metric belonging to a group of ratios called **efficiency ratios**. The calculation measures the average amount of time it takes for a business to collect money owed from the responsible party for services rendered and billed.

As its name implies, the unit of measurement employed by this particular metric is days, or rather the average number of days from the moment a physician provides a service until the patient or guarantor pays for that service. This number can tell you much about the financial health of the business.

Days in Accounts Receivable (DAR)
A growing number of days in AR is symptomatic of a faulty billing process. One way to determine DAR is to count days from the date of service to the date of payment for every claim, and then average that across all claims. A simpler way to compute average days in AR is by taking a ratio of AR to average daily charges, or

Days in AR = (Accounts Receivable / Average Charge) x 365

This metric also depends on the medical specialty, patient demographics, payer mix, and CPT sample. Another downside is that this metric is sensitive to the provider because it counts the lag time of unsubmitted claims for services already delivered. This lag time roughly averages across all payers, making DAR an effective comparison metric between payers for an individual provider, but invalidating it across multiple providers. One obvious advantage of the DAR metric is its independence of charges. The averaging feature eliminates sensitivity to a specific day or CPT, but it also hides the behavior shape of the AR curve.


The formula for calculating $dar$ is:

${dar} = \dfrac {earb} {{gct} \div {ndip}}$

<br>

Where:

   - ${ndip} = $ Number of Days in Period
   - ${gct} = $ Total Gross Charges
   - ${earb} = $ Ending AR Balance

[^1]: A list of fees physicians establish as the fair price for the services they provide. Keep in mind, this is *not* the same as a payment schedule.

### Number of Days in the Period

The number of days within the period for which you are measuring Days in AR. DAR is typically measured in monthly and quarterly increments, so this number will usually hover around 30, 60, 90, etc.

### Total Gross Charges

Gross charges, which are the *full* fee schedule charges[^2], are all charges generated by the practice, regardless of actual reimbursement. The Gross Charges figure is the total dollar amount charged during the Number of Days in the Period that you are measuring. Whether billed to insurance on a claim or to a self-pay patient, all charges for the period are included here.

[^2]: A list of fees physicians establish as the fair price for the services they provide. Keep in mind, this is *not* the same as a payment schedule.

### Ending AR Balance

This is the Accounts Receivables balance at the close of business (COB) on the final day of the Period that you are measuring. This figure is the total amount of money owed to the practice by patients, insurance companies, or other entities for services rendered. 

### Example Calculation

Let's say you have the following data:

   * Number of Days in Period = __30__
   * Total Gross Charges = __$180,000__
   * Ending AR Balance = __$77,400__

The calculation would look like this:

$\dfrac {77,400} {180,000 \div 30} = 12.9$

Or, in `R`:

```{r}
dar <- function(earb, gct, ndip) {
  earb / (gct / ndip)
}

dar(earb = 77400, 
    gct  = 180000, 
    ndip = 30)
```


## DAR Targets

   - $earb_t = (dar_t \times gct) \div ndip$ 
   - $gct_t = (earb \times ndip) \div dar_t$
   - $ndip_t = (dar_t \times gct) \div earb$
   - $dar_t = (earb \times ndip) \div gct$
